Testing and Isolation Efficacy:\\Insights from a Simple Epidemic Model

### 2021-06-23 SIR_manuscript.tex
authors and affiliation added

\documentclass[12pt]{article}
\usepackage{natbib}
\usepackage{hyperref}
\usepackage{grffile}
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{amssymb,amsmath,amsthm}
\usepackage{xcolor}
\usepackage{xspace}
\usepackage[nameinlink,capitalize]{cleveref}
\usepackage{cleveref}
\usepackage[margin=1in]{geometry}
\usepackage{lineno}\renewcommand\thelinenumber{\color{gray}\arabic{linenumber}}
\usepackage{pdflscape}
\usepackage{enumerate}

@@

\title{Testing and Isolation Efficacy:\\Insights from a Simple Epidemic Model}
\author{\david{??? authors ??? affiliations ???}}

>>>>

\documentclass[12pt]{article}
\usepackage{natbib}
\usepackage{hyperref}
\usepackage{grffile}
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{amssymb,amsmath,amsthm}
\usepackage{xcolor}
\usepackage{xspace}
\usepackage[nameinlink,capitalize]{cleveref}
\usepackage{cleveref}
\usepackage[margin=1in]{geometry}
\usepackage{lineno}\renewcommand\thelinenumber{\color{gray}\arabic{linenumber}}
\usepackage{pdflscape}
\usepackage{enumerate}
\usepackage{authblk}

@@

\title{Testing and Isolation Efficacy:\\Insights from a Simple Epidemic Model}
\author[1]{Ali Gharouni}
\author[1]{Fady M. Abdelmalek}
\author[1,2,3]{Benjamin M. Bolker}
\author[2,4,3]{Jonathan Dushoff}
\author[3,1,5]{David J. D. Earn}

\affil[1]{Department of Mathematics \& Statistics, McMaster University, Hamilton, Canada}
\affil[2]{Department of Biology, McMaster University, Hamilton, Canada}
\affil[3]{Michael G. DeGroote Institute for Infectious Disease Research, McMaster University, Hamilton, Canada}
\affil[4]{South African Centre for Epidemiological Modelling and Analysis, University of Stellenbosch, Stellenbosch, South Africa}
\affil[5]{Department of Mathematics, University of Toronto, Toronto, Canada}
